SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-03 scipy-1.0/covlett.tex
Update scipy-1.0/covlett.tex
Co-Authored-By: Joel Nothman <joel.nothman@gmail.com>
Update scipy-1.0/covlett.tex
Co-Authored-By: Alessandro Pietro Bardelli <apbard@users.noreply.github.com>

We are submitting the enclosed manuscript describing a milestone
1.0 release of SciPy for consideration to be published in
\emph{Scientific Reports}. SciPy is the fundamental scientific 
algorithm computing library in the Python programming language. 
Hundreds of experts have contributed to our library, which
has been download millions of times and has over 100,000 dependent
code repositories.

>>>>

We are submitting the enclosed manuscript describing a milestone
1.0 release of SciPy for consideration to be published in
\emph{Scientific Reports}. SciPy is the fundamental scientific 
computing library in the Python programming language. 
Hundreds of experts have contributed to our library, which
has been downloaded millions of times and has over 100,000 dependent
code repositories.
